Uncertainty propagation in deep neural networks for sparse coding

### 2018-03-10 paper/BayesianLISTA.tex
fontsize on figures is enlarged

\begin{figure}[t]
\centering
%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
%~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_valid}}
%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
%~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_valid}}
\caption{Predictive performance on number of iterations on the \textsc{mnist} data with dictionary size $K = 100$}
\label{fig:mnist_100}
\end{figure}

\begin{figure}[t]
\centering
%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_train}}
%~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_valid}}
%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
%~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_valid}}
\caption{Predictive performance on number of iterations on the \textsc{mnist} data with dictionary size $K = 250$}
\label{fig:mnist_250}
\end{figure}

>>>>

\begin{figure}[t]
\centering
%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
%~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_nmse_valid}}
%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
%~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_f_measure_valid}}
\caption{Predictive performance on number of iterations on the \textsc{mnist} data with dictionary size $K = 100$}
\label{fig:mnist_100}
\end{figure}

\begin{figure}[t]
\centering
%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_train}}
%~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_non_normalised_nmse_valid}}
%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
%~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_non_normalised_f_measure_valid}}
\caption{Predictive performance on number of iterations on the \textsc{mnist} data with dictionary size $K = 250$}
\label{fig:mnist_250}
\end{figure}
